Autogenerated Questions Paper Draft

### 2018-04-26 paper_draft/paper_draft.tex
Finish some todo's with revision (mostly style)

\usepackage{courier}
\usepackage{listings}
\lstset{basicstyle=\ttfamily, language=C++}

@@

\section{Abstract}

\section{Problem Description}

@@

\section{Input/output Flow}

Given the executable file and a templated file for input, it becomes extremely easy to generate any number of questions
repeatedly. In most cases, we wish to generate a single category of questions at a time, and this is the basis for the
overall structure of the main program. It simply checks the user's input from the predefined file to read basic inputs
such as the Main Category and Subcategory names (for identification in our CMS, Moodle), the filename for output, the number of
total questions to generate, the question set -- or category -- to generate from (such as Arrays, Functions, etc.),
the base difficulty, and the max difficulty of questions. By having this input file, it becomes easy to slightly modify
any parameters and repeatedly run the program.

@@

\section{Common Functions}

Each question, regardless of category, follows the same format: the title (including unique question number),
a prompt to explain the question, the right answer, and a number of wrong answers that can vary between categories.
A standard question in GIFTis shown below.

\begin{Verbatim}[tabsize=4]
::Dynamic Expressions Level 1 #005::
What is the variable "size" equal to?
<pre> int item = 4; 
int size = item / 3 - 3;</pre>
	{ 
	=-2 
	~-0.5 
	~-1.667 
	~1.5 
	~0 
	}
\end{Verbatim}

The title at the beginning (enclosed by two colons on each side) contains the subcategory name, "level" (i.e. difficulty) and a unique number (simply the current number
of questions generated in this batch). This information is necessary in Moodle to differentiate between 1) different question banks (e.g. "Dynamic Expressions Level 1") and
2) different questions within the question bank (e.g. \#005 vs. \#006). For this reason, it is recommended that only one output file per category be used to avoid any confusion
in the naming of question banks on Moodle.

The answer bank at the end (enclosed by the braces) contains all answer options for the question. The correct answer is preceded by the "=" and all wrong answers are denoted by
the "\~". When either of these identifiers is used, a answer is taken to be any text until a line break.

@@

The reason we have chosen GIFT as the output markup language to these questions -- as opposed to pure HTML or XML -- is for a number of reasons: 1) this language was constructed specifically for use in our CMS, Moodle (footnote: \url{https://docs.moodle.org/23/en/GIFT_format}); 2) GIFT has very minimal syntax, which allows it to be easily parsed and read by humans, which is useful when quickly evaluating the questions; and 3) similar to other courses (Generating Practice Questions as a Preparation Strategy
for Introductory Programming Exams), the instructors of this paper require students to construct their own multiple choice questions that may be used in a real exam. The reason we chose Moodle is because of its support through our institution. (TODO: should I mention this either?)

@@

\subsection{Difficulty}

@@

The most simple case of difficulty is found in the Expressions category (see Expressions below)
that simply serves to test a student's understanding of integer operations and variable assignment in programming.
Each difficulty is the same essential type of question, but the number of operands increases with increasing difficulty.
Some may consider this a naive approach to difficulty, but it is effective and showcases the fundamental relation
between question categories and difficulties.

Other question categories -- take Switch Cases, for example -- don't exhibit such a straightforward
notion of difficulty, but still an interesting example. Still, each difficulty is essentially the same where students are tested on their
ability to follow the control flow of a switch case statement by determining the final value of a variable (see Switch Cases for more detail).
The first difficulty randomly generates break statements (for each case) and it may or may not include a default case, where the second difficulty
always includes a break statement for each case and automatically includes a default case. Each difficulty of the Switch Case category follows the
same pattern by simply modifying random elements of the same core quesiton. While one may seem like more common -- but not necessarily always
correct -- example of a switch case block, it seems difficult to argue that one is inherently more "difficult" than another. However, it is clear
that each difficulty of this category would be beneficial to test in its own right, while still being able to test students fairly.

In contrast to these categories that implement the same essential question with slight changes, some categories (such as Functions
or Arrays), hold completely different questions in each difficulty. Here, a descriptor like "subcategory" seems more appropriate
(since it becomes harder to evaluate question on difficulty in relation to a different question), but
to avoid confusion, we will continue to reference these subcategories as difficulties. At first, it also seems like these questions shouldn't
be included in the same category, as each may be warranted their own category. However, because each relates to the same question bank category
(by testing the same fundamental concept) and any less or extra randomization in the question would not provide anything beneficial, but rather would shift focus from the objective of the question. We won't discuss in detail how a level of randomness affects
a question, but there is a certain amount of randomness in a question that no longer serves the purpose of making a question unique,
but instead it makes a question unnecessarily difficult to comprehend. In short, these different difficulties are not substantial enough to
create their own category and are similar enough to each other to be included in the same category.

Although it now may seem that this concept of difficulty is unclear and unfocused, it is important to note that each of these in Moodle are
formed as their own question bank, meaning students are each given questions from the same bank (therefore the same difficulty), and are not simply given questions within the same category, which suggests that different students receive different difficulties. The instructor then has the option of using whichever question bank (i.e. difficulty) is most appropriate,
and it offers a fair test to each student. Overall, it gives the instructor more choice on how to exactly test his or her students.

\subsection{Convincing Distractors}

@@

This notion is also present in other systems (Generating Diagnostic Multiple Choice Comprehension Cloze Questions), but with varying success. This implementation is novel for similar systems based on deterministic methods (pharmacy reference). Between categories, and sometimes between difficulties, there are different methods for generating distractors, specific to each question. We discuss all of the methods below within each category. Here are examples within a question using GIFT format.

\begin{Verbatim}
What is the variable "bar" equal to?
int foo = 2;
int bar = foo - 4 / 3 + 4;
{
	=5
	~4
	~4.67
	~2
	~3.33
}
\end{Verbatim}

@@

\subsection{Unique Answer Guarantee}

@@

Producing unique answers can become complicated is for two reasons: i) each category generates its own distractors using "clever" methods (e.g. evaluating an expression
without order of operations, or evaluating an expression based on wrong datatypes) and ii) complex answers
(in particular, answers containing vectors; see Arrays) become more difficult to compare and even more difficult
to generate an arbitrary new distractor (for the sake of uniqueness) that is still a somewhat plausible answer.
In the case of (i), it is fairly simple to compare all answers, and any distractors that are not unique are reassigned
a random value close to the answer. This is usually done with computational questions where the answer is simply a
numerical value. However, in the case of (ii), if we were to simply alter a value in the vector, the distractor would
become completely implausible because the answer only contains values that are originally in the array (see Arrays
Difficulty 1). It would make no sense at all to change a value in the array. In order to generate distractors that
are still plausible (but are guaranteed to be unique), we can simply shuffle the order of the vector. Yet, this has
another precondition that the number of permutations for the correct answer must be greater than or equal to the
number of available answers. Without this restraint, there would not be enough unique answers. If this is not met,
then it suffices to revert to the original strategy and simply assign a random value to the vector. Although it may
not be very convincing, unique distractors take precedence over plausible ones.

\subsection{Prevention of Trivial Cases}

@@

\section{Categories}

@@

There are four essential components we wish to answer with each of these categories: a) what is the goal of the question; what is it asking? b) an example question
(removed from GIFT format) for easy reference, c) what parts of the question are random? which of those parts are essential to the question (i.e. what
parts affect the answer or structure of the question)? which of those parts are non-essential (i.e. what parts have no affect over the question whatsoever)?
and are there any essential parts of the question that are not randomized (i.e. are there any constant factors of the question)? and lastly d) what methods
are used to generate the distractors? It is important to ask (a) so each question can have a definitive objective, and it should be easy to note if
certain randomness adds/hinders that objective or if the randomness does not preserve a comparable difficulty for different students.
This basically tries to prevent elements making a question "too random". It is also important to ask [TODO: should I include this part c? is it talked about enough later on?] (c) for a deep understanding of how the question
is randomized -- and how some parts are kept constant -- to produce independent yet similarly difficult questions. This part answers the main
methodology of all question generation. And as a consequence, (d) becomes relevant to ask to offer convincing distractors for a cohesive question.

@@

\subsection{Introductory Questions}
The categories included in this wave are identifiers, conditional expressions, and expressions. Each of these are topics are presented fairly early, and their main
focus includes -- explicitly and implicitly -- basic ideas such as syntax, variable access, integer operations, logical operations, and operator precedence.
Two of these categories (identifiers and conditional expressions) are simply true/false questions, so there are no sophisticated methods of generating
distractors, and this is part of the reason these categories are considered simple (from the point of view of implementation). However, these categories are still
worth discussing for their testing methods and more of a concrete introduction to the implementation. Let's take a detailed look at each category.

\subsubsection{Identifiers}

This first category is the simplest of all the questions here. The main objective of the question is to test students' knowledge on identifier syntax in C++.
All difficulties are also the same, just with a differing length of string, which only contributes a small amount to the essence of the question, so we'll consider
them all at once.
Here is an example of the true/false question:
\begin{Verbatim}
Is the following a valid C++ identifier?
Tb306wN 
\end{Verbatim}

@@

\subsubsection{Conditional Expressions}
This category is also fairly simple, mostly because it is another true/false question, but it does introduce some of the structure that we will reuse in other
categories (mostly the expression structure). The aim for this category is to have students evaluate a conditional expression, which tests logical operations
and their precedence. It also implicitly tests variable access, but this concept should be understood by this point, and it does not affect the question greatly.
Here is an example:

\begin{Verbatim}
What is the result of the following logical expression? 
int numbers = 3; 
int marks = 8; 
(numbers <= 4) == (marks <= 10) 
\end{Verbatim}

The only important random elements are the operand values (each is between 1 and 10) and all operators. It should first be noted that the structure of the expression
is always in the form of 
\begin{Verbatim}
(< sub-expression >) < logical operator > (< sub-expression >)
\end{Verbatim}
where each sub-expression is of the form 
\begin{Verbatim}
< variable > < comparison op > < literal >
\end{Verbatim}
Each comparison operator is chosen randomly from \verb;(>, >=, <, <=); and each logical operator is chosen randomly from \verb;(==, !=, &&, ||);.

Each difficulty does not differ greatly from the other. Difficulties 1 and 3 always have 2 sub-expressions, and difficulties 2 and 4 always have 3. And the other
difference between difficulties 1 and 2 from 3 and 4 is that the latter two difficulties have a random order of operands in the expression. For example,

\begin{lstlisting}
int documents = 8;
int bar = 10;
(bar <= documents) != (10 < 9)
\end{lstlisting}

@@

\subsubsection{Expressions}
This category is arguably the most important of all, as it serves as a basis for all other, more complex categories, and it is even utilized in other other categories
(namely Functions). It still follows the basic structure as Identifiers and Conditional expressions (with simple prompts), but it introduces methods used to generate convincing distractors.
The main aim is to test students' ability to evaluate simple arithmetic expressions in C++ using integer operands and operations. Similar to Conditional Expressions, it also
tests minor variable accessing. Here is an example:

\begin{lstlisting}
What is the variable "bar" equal to? 
int foo = 2; 
int bar = foo * 4 % 3 + 7; 
\end{lstlisting}

@@

In this instance, the four distractor methods alter how the expression is evaluated by 1) disregarding order of operations, 2) using float values and operations, 3) evaluating the expression from
right to left, and 4) disregarding the order of operations and using the float values (a combination of 1 and 2). These methods, while not particularly novel or sophisticated, aid the main objective 
of the question in their deliberate misunderstanding of the main concepts. For example, any student that is unfamiliar with integer operations is certain to select the distractor provided by method 2. Of course, in some cases, certain methods would not provide a different answer than the correct one (as integer addition and float addition are similar, etc.), however different answers are still guaranteed by the unique answer checking (see Unique Answer Guarantee above).

\subsection{Loops}

This wave of questions is usually offered to students next, although -- implementation wise -- it doesn't have many similarities to the previous wave other than general format. Instead, Loops provides 
a general template for all of its own categories. Since we may wish to test all types of loops (we will only consider for loops, while loops, and do while loops), we can create a general base for 
all types of loops and test the same questions in each (as the main difference between each is mostly syntax). We separate each of these loops by category so instructors have the option of 
choosing exactly what kind of loop they wish to test. Instead of outlining each category as in the previous wave, we will outline two different types of questions (called Loop Counting and Loop Printing) that then create a category for each type of loops (6 categories total). Implementation between categories of the same question type (e.g. For Loops Counting vs. While Loops Counting) have virtually the same implementation (except for an edge case in do while loops as readers can imagine), so we will not distinguish between them and instead only talk of the different question types.

\subsubsection{Loop Counting}

This first question type of loops is probably similar to questions used in most introductory programming courses, as it is the fundamental concept behind loops (especially for loops). Simply, these
questions ask a student how many times a statement within a for loop is executed, based on the common structure of a "counter" variable that is updated each loop, and then compared to a
terminating condition: the same structure as a for loop. This is the essence of the question at each difficulty, however, due to the many dependent parts of the question, many different forms 
of randomization (mostly pertaining to the domain) occur between each difficulty, hence the distinction.

\paragraph{Difficulty 1} \hfill \par
This difficulty is the most common form of for loops, and, even to some new students, can be trivial to evaluate. However, it still ensures that the main concepts of loop syntax, terminating 
conditions, and updating statements. Here is an example from the For Loops category:

\begin{lstlisting}
How many times does the '*' print? 
for (int b = 4; b < 7; b = b + 1)
{
	cout << '*';
} 
\end{lstlisting}

@@

\paragraph{Difficulty 2} \hfill \par
To increase the effort, more comparison operators \verb;(>, >=, <, <=); are used for the terminating condition, and the subtraction operator is used in the update
statement. Here is an example from the Do While Loops category.

\begin{lstlisting}
How many times does the '*' print? 
int j = 53;
do 
{
	cout << '*'; 
	j = j - 5; 
} while (j >= 30); 
\end{lstlisting}

@@

\paragraph{Difficulty 3} \hfill \par
Using the same structure as the previous difficulty, the most significant difference is that the update statements use the multiplication and division operators as opposed to the addition
and subtraction operators. Here is an example from the While Loops category.

\begin{lstlisting}
How many times does the '*' print?
int i = 13; 
while (i >= 3) 
{
	cout << '*'; 
	i /= 2;
}
\end{lstlisting}

@@

\paragraph{Difficulty 4} \hfill \par
While still offering the main objective of all of these difficulties, this difficulty can appear to be fundamentally different. It uses the same generation methods as Difficulty 2, except it uses 
a nested loop for execution instead of a single loop. Here is a concrete example from the For Loops category.

\begin{lstlisting}
How many times does the '*' print? 
for (int i = 43; i >= 20; i = i - 10) 
{ 
	for (int j = 56; j > 45; j = j - 5) 
	{ 
		cout << '*'; 
	} 
}
\end{lstlisting}

@@

\subsubsection{Loop Printing}

This next type of question in the Loops categories contains similarities to Loop Counting. It aims at the same essence, but it tries to test a deeper understanding of loops by printing out the 
``counter'' variable at each iteration. Implicitly, it still tests the number of iterations the loop executes, but the main objective is to understand, explicitly, when a variable is incremented,
how integer operations affect the update, and the value that makes the loop terminate. For the sake of questions not being too difficult, each loop only executes between 3 and 5 iterations, and there is no fourth difficulty including nested loops. Here is an example from the Do While Loops category.

\begin{lstlisting}
What is the following output of the code? 
int b = 61; 
do
{ 
	cout << b << ' '; 
	b = b - 10; 
} while (b > 20); 
\end{lstlisting}

Each difficulty is generated using the exact same methods as Loop Counting but obviously has different distractor methods, yet the same distractors are used for each difficulty. The first 
distractor uses all of the same values as the correct answer, except it omits the first value. The second distractor uses the same values as the correct answer, but it appends one more iteration
from the loop. The third distractor is the same values as the correct one, except it omits the last value. Finally, the fourth distractor combines the first two methods by omitting the first value
and appends an extra iteration to the end. While there are many options for generating distractors, these all seem to provide convincing answers that some students may create on their own.

\subsection{Advanced}

While this wave is not particularly more difficult than the others, we will refer to them as advanced because they are usually introduced near the end of a course, and they some categories also 
utilize other earlier categories. Some of these difficulties also use very involved methods for question generation, evaluation, and distractor generation -- as well as the unique answer guarantee 
for Arrays as discussed earlier.

\subsubsection{Switch Cases}
The first category in this wave has the same essence for each difficulty; the only significant differences are the random elements, which then determine the difficulty. This is similar to the Loop 
Counting types described before. For the sake of brevitiy, here is a description of all shared aspects, and we will later discuss each difficulty's subtleties. First, a general example:

\begin{lstlisting}
What is the value of "bar" after the switch case block?
int bar = 4; 
switch (bar) { 
	case 2: 
		bar = 5; 
		break; 
	case 4: 
		bar = 6; 
	case 1: 
		bar = 2;
		break; 
	case 3: 
		bar = 0; 
	case 0: 
		bar = 1; 
		break; 
} 
\end{lstlisting}

@@

\subsubsection{Arrays}

>>>>

\usepackage{courier}
\usepackage{listings}
\lstset{basicstyle=\ttfamily, language=C++, captionpos=b}

@@

\section{Abstract} \label{sec-abstract}

\section{Problem Description} \label{sec-problem_description}

@@

\section{Input/output Flow} \label{sec-input/output_flow}

Given the executable file and a templated file for input, it becomes extremely easy to generate any number of questions
repeatedly. In most cases, we wish to generate a single category of questions at a time, and this is the basis for the
overall structure of the main program. It simply checks the user's input from the predefined file to read basic inputs
such as the main category and subcategory names (for identification in our CMS, Moodle), the filename for output, the number of
total questions to generate, the question set -- or category -- to generate from (such as \textbf{Arrays}, \textbf{Functions}, etc.),
the base difficulty, and the max difficulty of questions. By having this input file, it becomes easy to slightly modify
any parameters and repeatedly run the program.

@@

\section{Common Functions} \label{sec-common_functions}

Each question, regardless of category, follows the same format: the title (including unique question number),
a prompt to explain the question, the right answer, and a number of wrong answers that can vary between categories.
A standard question in GIFT is shown below.
\begin{hbox}{}
\begin{lstlisting}[language=, caption={A full question in GIFT format.}, label={lst-gift}]	%use no specfic language here because it is in GIFT format
::Dynamic Expressions Level 1 #005::
What is the variable "size" equal to?
<pre> int item = 4; 
int size = item / 3 - 3;</pre>
	{ 
	=-2 
	~-0.5 
	~-1.667 
	~1.5 
	~0 
	}
\end{lstlisting}
\end{hbox}

The title at the beginning (enclosed by two colons on each side) contains the subcategory name, ``level" (i.e. difficulty) and a unique number (simply the current number
of questions generated in this batch). This information is necessary in Moodle to differentiate between different question banks (e.g. ``Dynamic Expressions Level 1") and different questions within the question bank (e.g. \#005 vs. \#006). For this reason, it is recommended that only one output file per category be used to avoid any confusion
in the naming of question banks on Moodle.

The answer bank at the end (enclosed by the braces) contains all answer options for the question. The correct answer is preceded by the ``=" and all wrong answers are denoted by
the ``$\sim$". When either of these identifiers is used, a answer is taken to be any text until a line break.

@@

The reason we have chosen GIFT as the output markup language to these questions -- as opposed to pure HTML or XML -- is for a number of reasons: this language was constructed specifically for use in our CMS, Moodle (footnote: \url{https://docs.moodle.org/23/en/GIFT_format}); GIFT has very minimal syntax, which allows it to be easily parsed and read by humans, which is useful when quickly evaluating the questions; and, similar to other courses (Generating Practice Questions as a Preparation Strategy
for Introductory Programming Exams), the instructors of this paper require students to construct their own multiple choice questions that may be used in a real exam. The reason we chose Moodle is because of its support through our institution. (TODO: should I mention this either?)

@@

\subsection{Difficulty} \label{sec-difficulty}

@@

A simple and informative example of difficulty is found in the \textbf{Expressions} category (see section \ref{subsubsec-expressions})
that simply serves to test a student's understanding of integer operations and variable assignment in programming.
Each difficulty is the same essential type of question, but the number of operands increases with increasing difficulty.
Some may consider this a naive approach to difficulty, but it is effective and showcases the fundamental relation
between question categories and difficulties.

Other question categories -- take \textbf{Switch Cases}, for example -- don't exhibit such a straightforward
notion of difficulty, but still offer interesting examples. Each difficulty tests students on the same essential concept of
the control flow of a switch case statement by assigning a value to a variable (see section \ref{subsubsec-switch_cases} for more detail).
The first difficulty randomly generates break statements (for each case) and it may or may not include a default case, where the second difficulty
always includes a break statement for each case and automatically includes a default case. Each difficulty of the \textbf{Switch Cases} category follows the
same pattern by simply modifying random elements of the same core quesiton. While one may seem like more common -- but not necessarily always
correct -- example of a switch case block, it seems difficult to argue that one is inherently more "difficult" than another. However, it is clear
that each difficulty of this category would be beneficial to test in its own right, while still being able to test students fairly.

In contrast to these categories that implement the same essential question with slight changes, some categories (such as \textbf{Functions}
or \textbf{Arrays}), hold completely different questions in each difficulty. Here, a descriptor like "subcategory" seems more appropriate
(since it becomes harder to evaluate question on difficulty in relation to a different question), but
to avoid confusion, we will continue to reference these subcategories as difficulties. At first, it also seems like these questions shouldn't
be included in the same category, as each may be warranted their own category. However, because each relates to the same question bank category
(by testing the same fundamental concept) and any less or extra randomization in the question would not provide anything beneficial, but rather would shift focus from the objective of the question. We won't discuss in detail how a level of randomness affects
a question, but there is a certain amount of randomness in a question that no longer serves the purpose of making a question unique,
but instead it makes a question unnecessarily difficult to comprehend. In short, these different difficulties are not substantial enough to
create their own category and are similar enough to each other to be included in the same category.

Although it now may seem that this concept of difficulty is unclear and unfocused, it is important to note that each of these in Moodle are
formed as their own question bank, meaning students are each given questions from the same bank (therefore the same difficulty) and are not simply given questions of arbitrary difficulty within the same category, which suggests that different students receive different difficulties. The instructor then has the option of using whichever question bank (i.e. difficulty) is most appropriate,
and it offers a fair test to each student. Overall, it gives the instructor more choice on how to exactly test his or her students.

\subsection{Convincing Distractors} \label{sec-convincing_distractors}

@@

This notion is also present in other systems (Generating Diagnostic Multiple Choice Comprehension Cloze Questions), but with varying success. This implementation is novel for similar systems based on deterministic methods (pharmacy reference). Between categories, and sometimes between difficulties, there are different methods for generating distractors, specific to each question. We discuss all of the methods below within each category. Here are examples within a question using GIFT format.
\begin{hbox}{}
\begin{lstlisting}[breaklines=true, caption={A question with distractors in GIFT format.}, label=lst-distractors]
What is the variable "bar" equal to?
int foo = 2;
int bar = foo - 4 / 3 + 4;
{
	=5
	~4
	~4.67
	~2
	~3.33
}
\end{lstlisting}
\end{hbox}

@@

\subsection{Unique Answer Guarantee} \label{sec-unique_answer_guarantee}

@@

TODO: do a fancy list thing here
Producing unique answers can become complicated is for two reasons: i) each category generates its own distractors using ``clever" methods (e.g. evaluating an expression
without order of operations, or evaluating an expression based on wrong datatypes) and ii) complex answers
(in particular, answers containing vectors as in \textbf{Arrays}) become more difficult to compare and even more difficult
to generate an arbitrary new distractor (for the sake of uniqueness) that is still a somewhat plausible answer.
In the case of (i), it is fairly simple to compare all answers, and any distractors that are not unique are reassigned
a random value close to the answer. This is usually done with computational questions where the answer is simply a
numerical value. However, in the case of (ii), if we were to simply alter a value in the vector, the distractor would
become completely implausible because the answer only contains values that are originally in the array (see \textbf{Arrays Difficulty 3} in section \ref{subsubsec-arrays}). 
It would make no sense at all to change a value in the array. In order to generate distractors that
are still plausible (but are guaranteed to be unique), we can simply shuffle the order of the vector. Yet, this has
another precondition that the number of permutations for the correct answer must be greater than or equal to the
number of available answers. Without this restraint, there would not be enough unique answers. If this is not met,
then it suffices to revert to the original strategy and simply assign a random value to the vector. Although it may
not be very convincing, unique distractors take precedence over plausible ones.

\subsection{Prevention of Trivial Cases} \label{sec-prevention_of_trivial_cases}

@@

\section{Categories} \label{sec-categoires}

@@

TODO: another fancy list thing here
There are four essential components we wish to answer with each of these categories: a) what is the goal of the question; what is it asking? b) an example question
(removed from GIFT format) for easy reference, c) what parts of the question are random? which of those parts are essential to the question (i.e. what
parts affect the answer or structure of the question)? which of those parts are non-essential (i.e. what parts have no affect over the question whatsoever)?
and are there any essential parts of the question that are not randomized (i.e. are there any constant factors of the question)? and lastly d) what methods
are used to generate the distractors? It is important to ask (a) so each question can have a definitive objective, and it should be easy to note if
certain randomness adds/hinders that objective or if the randomness does not preserve a comparable difficulty for different students.
This basically tries to prevent elements making a question "too random". It is also important to ask [TODO: should I include this part c? is it talked about enough later on?] (c) for a deep understanding of how the question
is randomized -- and how some parts are kept constant -- to produce independent yet similarly difficult questions. This part answers the main
methodology of all question generation. And as a consequence, (d) becomes relevant to ask to offer convincing distractors for a cohesive question.

@@

\subsection{Introductory Questions} \label{subsec-introductory_questions}
The categories included in this wave are \textbf{Identifiers}, \textbf{Conditional Expressions}, and \textbf{Expressions}. Each of these are topics are presented fairly early, and their main
focus includes -- explicitly and implicitly -- basic ideas such as syntax, variable access, integer operations, logical operations, and operator precedence.
The first two categories are simply true/false questions, so there are no sophisticated methods of generating
distractors, and this is part of the reason these categories are considered simple (from the point of view of implementation). However, these categories are still
worth discussing for their testing methods and more of a concrete introduction. Let's take a detailed look at each category.

\subsubsection{Identifiers} \label{subsubsec-identifiers}

This first category is the simplest of all the questions here. The main objective of the question is to test students' knowledge on identifier syntax in C++.
All difficulties are also the same, just with a differing length of string, which only contributes a small amount to the essence of the question, so we'll consider
them all at once.
Here is an example of the true/false question:
\begin{hbox}{}
\begin{lstlisting}[breaklines=true, caption={A question on identifiers.}, label=lst-identifiers]
Is the following a valid C++ identifier?
Tb306wN 
\end{lstlisting}
\end{hbox}

@@

\subsubsection{Conditional Expressions} \label{subsubsec-condtional_expressions}
This category is also fairly simple, mostly because it is another true/false question, but it does introduce some of the structure that we will reuse in other
categories (mostly the expression structure). The aim for this category is to have students evaluate a conditional expression, which tests logical operations
and their precedence. It also implicitly tests variable access, but this concept should be understood by this point, and it does not affect the question greatly.
Here is an example:
\begin{hbox}{}
\begin{lstlisting}[breaklines=true, caption={Conditional Expressions Question}, label=lst-condtionals_1]
What is the result of the following logical expression? 
int numbers = 3; 
int marks = 8; 
(numbers <= 4) == (marks <= 10) 
\end{lstlisting}
\end{hbox}

The only important random elements are the operand values (each is between 1 and 10) and all operators. It should first be noted that the structure of the expression
is always in the form of 
\begin{Verbatim}
(<sub-expression>) <logical operator> (<sub-expression>)
\end{Verbatim}
where each sub-expression is of the form 
\begin{Verbatim}
<variable> <comparison operator> <literal>
\end{Verbatim}
Each comparison operator is chosen randomly from \verb;(>, >=, <, <=); and each logical operator is chosen randomly from \verb;(==, !=, &&, ||);.

Each difficulty does not differ greatly from the other. Difficulties 1 and 3 always have 2 sub-expressions, and difficulties 2 and 4 always have 3 sub-expressions. The other
difference between difficulties 1 and 2 from 3 and 4 is that the latter two difficulties have a random order of operands in the expression. For example,
\begin{hbox}{}
\begin{lstlisting}[breaklines=true]
int documents = 8;
int bar = 10;
(bar <= documents) != (10 < 9)
\end{lstlisting}
\end{hbox}

@@

\subsubsection{Expressions} \label{subsubsec-expressions}
This category is arguably the most important of all, as it serves as a basis for all other, more complex categories, and it is even utilized in other other categories
(namely \textbf{Functions}). It still follows the basic structure as \textbf{Identifiers} and \textbf{Conditional Expressions} (with simple prompts), but it introduces methods used to generate convincing distractors.
The main aim is to test students' ability to evaluate simple arithmetic expressions in C++ using integer operands and operations. Similar to \textbf{Conditional Expressions}, it also
tests minor variable accessing. Here is an example:
\begin{hbox}{}
\begin{lstlisting}[breaklines=true]
What is the variable "bar" equal to? 
int foo = 2; 
int bar = foo * 4 % 3 + 7; 
\end{lstlisting}
\end{hbox}

@@

TODO: fancy list thing below

In this instance, the four distractor methods alter how the expression is evaluated by 1) disregarding order of operations, 2) using float values and operations, 3) evaluating the expression from
right to left, and 4) disregarding the order of operations and using the float values (a combination of 1 and 2). These methods, while not particularly novel or sophisticated, aid the main objective 
of the question in their deliberate misunderstanding of the main concepts. For example, any student that is unfamiliar with integer operations is certain to select the distractor provided by method 2. Of course, in some cases, certain methods would not provide a different answer than the correct one (as integer addition and float addition are similar, etc.), however different answers are still guaranteed by the unique answer checking (see Unique Answer Guarantee in section \ref{sec-unique_answer_guarantee}).

\subsection{Loops} \label{subsec-loops}

This wave of questions is usually offered to students next, although -- implementation wise -- it doesn't have many similarities to the previous wave other than general format. Instead, \textbf{Loops} provides 
a general template for all of its own categories. Since we may wish to test all types of loops (we will only consider for loops, while loops, and do while loops), we can create a general base for 
all types of loops and test the same questions in each (as the main difference between each is mostly syntax). We separate each of these loops by category so instructors have the option of 
choosing exactly what kind of loop they wish to test. Instead of outlining each category as in the previous wave, we will outline two different types of questions (called \textbf{Loop Counting} and \textbf{Loop Printing}) that then create a category for each type of loops (6 categories total). Implementation between categories of the same question type (e.g. For Loops Counting vs. While Loops Counting) have virtually the same implementation (except for an edge case in do while loops as readers can imagine), so we will not distinguish between them and instead only talk of the different question types.

\subsubsection{Loop Counting} \label{subsubsec-loop_counting}

This first question type of loops is probably similar to questions used in most introductory programming courses, as it is the fundamental concept behind loops (especially for loops). Simply, these
questions ask a student how many times a statement within a for loop is executed, based on the common structure of a ``counter" variable that is updated each loop, and then compared to a
terminating condition: the same structure as a for loop. This is the essence of the question at each difficulty, however, due to the many dependent parts of the question, many different forms 
of randomization (mostly pertaining to the domain) occur between each difficulty, hence the distinction.

\paragraph{Difficulty 1} \hfill \par 
This difficulty is the most common form of for loops, and, even to some new students, can be trivial to evaluate. However, it still ensures that the main concepts of loop syntax, terminating 
conditions, and updating statements. Here is an example from the \textbf{For Loops} category:
\begin{hbox}{}
\begin{lstlisting}[breaklines=true]
How many times does the '*' print? 
for (int b = 4; b < 7; b = b + 1)
{
	cout << '*';
} 
\end{lstlisting}
\end{hbox}

@@

\paragraph{Difficulty 2} \hfill \par
To increase the effort, more comparison operators \verb;(>, >=, <, <=); are used for the terminating condition, and the subtraction operator is used in the update
statement. Here is an example from the \textbf{Do While Loops} category.
\begin{hbox}{}
\begin{lstlisting}[breaklines=true]
How many times does the '*' print? 
int j = 53;
do 
{
	cout << '*'; 
	j = j - 5; 
} while (j >= 30); 
\end{lstlisting}
\end{hbox}

@@

\paragraph{Difficulty 3} \hfill \par 
Using the same structure as the previous difficulty, the most significant difference is that the update statements use the multiplication and division operators as opposed to the addition
and subtraction operators. Below is an example from the \textbf{While Loops} category.
\begin{hbox}{}
\begin{lstlisting}[breaklines=true, float]
How many times does the '*' print?
int i = 13; 
while (i >= 3) 
{
	cout << '*'; 
	i /= 2;
}
\end{lstlisting}
\end{hbox}

TODO: maybe the list thing here

@@

\paragraph{Difficulty 4} \hfill \par 
While still offering the main objective of all of these difficulties, this difficulty can appear to be fundamentally different. It uses the same generation methods as Difficulty 2, except it uses 
a nested loop for execution instead of a single loop. Here is a concrete example from the \textbf{For Loops} category.
\begin{hbox}{}
\begin{lstlisting}[breaklines=true]
How many times does the '*' print? 
for (int i = 43; i >= 20; i = i - 10) 
{ 
	for (int j = 56; j > 45; j = j - 5) 
	{ 
		cout << '*'; 
	} 
}
\end{lstlisting}
\end{hbox}

@@

\subsubsection{Loop Printing} \label{subsubsec-loop_printing}

This next type of question in the \textbf{Loops} categories contains similarities to \textbf{Loop Counting}. It aims at the same essence, but it tries to test a deeper understanding of loops by printing out the 
``counter'' variable at each iteration. Implicitly, it still tests the number of iterations the loop executes, but the main objective is to understand, explicitly, when a variable is incremented,
how integer operations affect the update, and the value that makes the loop terminate. For the sake of questions not being too difficult, each loop only executes between 3 and 5 iterations, and there is no fourth difficulty including nested loops. Here is an example from the Do While Loops category.
\begin{hbox}{}
\begin{lstlisting}[breaklines=true]
What is the following output of the code? 
int b = 61; 
do
{ 
	cout << b << ' '; 
	b = b - 10; 
} while (b > 20); 
\end{lstlisting}
\end{hbox}

Each difficulty is generated using the exact same methods as \textbf{Loop Counting} but obviously has different distractor methods, yet the same distractors are used for each difficulty. The first 
distractor uses all of the same values as the correct answer, except it omits the first value. The second distractor uses the same values as the correct answer, but it appends one more iteration
from the loop. The third distractor is the same values as the correct one, except it omits the last value. Finally, the fourth distractor combines the first two methods by omitting the first value
and appends an extra iteration to the end. While there are many options for generating distractors, these all seem to provide convincing answers that some students may create on their own.

\subsection{Advanced} \label{subsec-advanced}

While this wave is not particularly more difficult than the others, we will refer to them as advanced because they are usually introduced near the end of a course, and they some categories also 
utilize other earlier categories. Some of these difficulties also use very involved methods for question generation, evaluation, and distractor generation -- as well as the unique answer guarantee 
for \textbf{Arrays}.

\subsubsection{Switch Cases} \label{subsubsec-switch_cases}
The first category in this wave has the same essence for each difficulty; the only significant differences are the random elements, which then determine the difficulty. This is similar to the \textbf{Loop 
Counting} types described before. For the sake of brevitiy, here is a description of all shared aspects, and we will later discuss each difficulty's subtleties. First, a general example:
\begin{hbox}{}
\begin{lstlisting}[breaklines=true]
What is the value of "bar" after the switch case block?
int bar = 4; 
switch (bar) { 
	case 2: 
		bar = 5; 
		break; 
	case 4: 
		bar = 6; 
	case 1: 
		bar = 2;
		break; 
	case 3: 
		bar = 0; 
	case 0: 
		bar = 1; 
		break; 
} 
\end{lstlisting}
\end{hbox}

@@

\subsubsection{Arrays} \label{subsubsec-arrays}

This category (along with the \textbf{Functions} category) differs greatly from the other types of categories and poses an almost altogether different type of category. The main difference being how difficulties are defined within it. As mentioned above in the Difficulty section (\ref{sec-difficulty}), it is hard to alter a single aspect of these questions to make it more or less difficult, and
for that reason each single difficulty in this category is a different question altogether -- yet still ordered by their relative difficulty. Of course, all of these questions still pertain to array concepts
as a whole, and it is much easier to separate them and even use them in different settings. But here, the concept of difficulties is slightly different than what has been mentioned previously.
